CRUSE to Safe Cycling in Ireland

### 2023-09-29 paper.qmd
Improve discussion of evs

Recognizing the growing evidence of such impacts of poorly designed and performing transport systems, governments in many countries have set targets and taken actions.
In the context of climate, road safety and physicial inactivity crises, policies to improve transport systems can be classified according to the 'Avoid-Shift-Improve' (ASI) framework [@jaramillo2022].
The framework highlights the importance of demand reduction (*avoid*ing unnecessary trips), in addition to mode *shift* and *improvement* of existing energy converters, in that order.

Uptake of cycling, the main topic of this paper, should be seen in this broader context of transport decarbonisation [@brand2020] and sustainable mobility [@burns2013].
Although cycling uptake appears on the surface to only relate to the 'shift' part of the ASI framework, closer consideration of the knock-on impacts of cycling uptake shows that it can also help avoid unnecessary trips [@nello-deakin2020].
The rapid uptake of highly efficient e-bikes can also be seen as an improvement on most electric vehicles, which are too heavy and expensive to be a sustainable alternative and could in fact delay the transition away from car dependency and inadvertently enable "high travel lock-in" [@anable2019].
At the European level, the European Union has a target of reducing greenhouse gas emissions by 55% by 2030, compared to 1990 levels, and to achieve 'net-zero' by 2050.[^1]

>>>>

Recognizing the growing evidence of such impacts of poorly designed and performing transport systems, governments in many countries have set targets and taken actions.
In the context of climate, road safety and physicial inactivity crises, policies to improve transport systems can be classified according to the 'Avoid-Shift-Improve' (ASI) framework [@jaramillo2022].
The framework highlights the importance of demand reduction (*avoid*ing unnecessary trips), in addition to mode *shift* to sustainable modes and *improvement* of existing energy converters, in that order.

Uptake of cycling, the main topic of this paper, should be seen in this broader context of transport decarbonisation [@brand2020] and sustainable mobility [@burns2013].
Although cycling uptake appears on the surface to only relate to the 'shift' part of the ASI framework, closer consideration of the knock-on impacts of cycling uptake shows that it can also help avoid unnecessary trips [@nello-deakin2020].
Furthermore, highly efficient e-bikes --- which are seeing rapid uptake in Ireland and other countries --- outperform electric electric cars, which are too heavy and expensive.
Heavy electric cars could slow the transition away from car dependency and inadvertently enable "high travel lock-in" [@anable2019].
At the European level, the European Union has a target of reducing greenhouse gas emissions by 55% by 2030, compared to 1990 levels, and to achieve 'net-zero' by 2050.[^1]
